Time series clusters, k = 9

### 2021-03-25 src/descriptive_Clusters.Rmd
leftovers -- sorry

@@

#create time variation plots for speedtests for each year
Tests19 <- count(TS2019, date)
TS2019 <- left_join(TS2019, Tests19)
names(TS2019)[13] <- "test frequency 2019"
time.var.plot2019 <- timeVariation(TS2019, pollutant = "test frequency 2019", statistic = "mean")
Tests20 <- count(TS2020, date)
TS2020 <- left_join(TS2020, Tests20)
names(TS2020)[13] <- "test frequency 2020"
time.var.plot2020 <- timeVariation(TS2020, pollutant = "test frequency 2020", statistic = "mean")

#export time variation plots for paper
out.plot <- paste(path, "/paper/v1/figures/time.var.plot2019.png", sep = "")
png(out.plot)
time.var.plot2019
dev.off()

out.plot <- paste(path, "/paper/v1/figures/time.var.plot2020.png", sep = "")
png(out.plot)
time.var.plot2020
dev.off()

#join clusters to TS2020
names(clusters) [1] <- "LAD19NM"
TS2020 <- left_join(TS2020, clusters)
TS2019 <- left_join(TS2019, clusters)
#remove NAs? - otherwise cannot create unified dataframes for below stats

@@

```{r }
#summarise test frequency clusters by hour of each weekday and plot
cluster.tests <- TS2020 %>%
  group_by(cluster.tests, weekday, hour) %>%
  summarise(n.tests = n())
names(cluster.tests)[1] <- "clusterID"
cluster.tests$clusterID <- as.factor(cluster.tests$clusterID)
#add fake dates for plotting
help.dates <- tibble(help.date.time = c(
  make_datetime(year = 2020, month = 3, day = 2),
  make_datetime(year = 2020, month = 3, day = 3),
  make_datetime(year = 2020, month = 3, day = 4),
  make_datetime(year = 2020, month = 3, day = 5),
  make_datetime(year = 2020, month = 3, day = 6)),
                     weekday = c("Mon", "Tue", "Wed", "Thu", "Fri"))
cluster.tests <- merge(cluster.tests, help.dates, by = "weekday")
cluster.tests$hour <- paste(cluster.tests$hour, ":00", sep="")
cluster.tests$help.date.time <- with(cluster.tests, as.POSIXct(paste(help.date.time, hour), format="%Y-%m-%d %H:%M"))
#plot cluster statistic for number tests
TestCluster <- ggplot(cluster.tests, aes(help.date.time, n.tests, 
                                         colour = clusterID))
TestCluster + geom_line() + labs(x = "Weekdays March-May 2020") + 
  scale_x_datetime(breaks = as.POSIXct(c("2020-03-02 15:00:00", 
                    "2020-03-03 15:00:00", "2020-03-04 15:00:00",
                    "2020-03-05 15:00:00", "2020-03-06 15:00:00"), 
                    labels = "%a"), labels = 
                     c("Mon", "Tues", "Weds", "Thurs", "Fri")) + geom_point()
#summarise test frequency clusters by hour of each weekday 2019 and plot
cluster.tests19 <- TS2019 %>%
  group_by(cluster.tests, weekday, hour) %>%
  summarise(n.tests = n())
names(cluster.tests19)[1] <- "clusterID"
cluster.tests19$clusterID <- as.factor(cluster.tests19$clusterID)
#add fake dates for plotting
help.dates <- tibble(help.date.time = c(
  make_datetime(year = 2019, month = 3, day = 4),
  make_datetime(year = 2019, month = 3, day = 5),
  make_datetime(year = 2019, month = 3, day = 6),
  make_datetime(year = 2019, month = 3, day = 7),
  make_datetime(year = 2019, month = 3, day = 8)),
                     weekday = c("Mon", "Tue", "Wed", "Thu", "Fri"))
cluster.tests19 <- merge(cluster.tests19, help.dates, by = "weekday")
cluster.tests19$hour <- paste(cluster.tests19$hour, ":00", sep="")
cluster.tests19$help.date.time <- with(cluster.tests19, as.POSIXct(paste(help.date.time, hour), format="%Y-%m-%d %H:%M"))
#plot cluster statistic for number tests
TestCluster19 <- ggplot(cluster.tests19, aes(help.date.time, n.tests, 
                                         colour = clusterID))
TestCluster19 + geom_line() + labs(x = "Weekdays March-May 2019") + 
  scale_x_datetime(breaks = as.POSIXct(c("2020-03-02 15:00:00", 
                    "2020-03-03 15:00:00", "2020-03-04 15:00:00",
                    "2020-03-05 15:00:00", "2020-03-06 15:00:00"), 
                    labels = "%a"), labels = 
                     c("Mon", "Tues", "Weds", "Thurs", "Fri")) + geom_point()
#summarise upload speed clusters by hour of each weekday and plot
#plot largest 6 clusters - all over 500k pop
cluster.up <- TS2020 %>%
  group_by(cluster.up, weekday, hour) %>%
  summarise(mean.up = mean(speedup))
names(cluster.up)[1] <- "clusterID"
names(LAD.cluster.up)[1] <- "clusterID"
cluster.up <- left_join(cluster.up, LAD.cluster.up)
cluster.up <- cluster.up[which(cluster.up$up.LADs > 4),]
cluster.up$clusterID <- as.factor(cluster.up$clusterID)
#add fake dates for plotting
help.dates <- tibble(help.date.time = c(
  make_datetime(year = 2020, month = 3, day = 2),
  make_datetime(year = 2020, month = 3, day = 3),
  make_datetime(year = 2020, month = 3, day = 4),
  make_datetime(year = 2020, month = 3, day = 5),
  make_datetime(year = 2020, month = 3, day = 6)),
                     weekday = c("Mon", "Tue", "Wed", "Thu", "Fri"))
cluster.up <- merge(cluster.up, help.dates, by = "weekday")
cluster.up$hour <- paste(cluster.up$hour, ":00", sep="")
cluster.up$help.date.time <- with(cluster.up, as.POSIXct(paste(help.date.time, hour), format="%Y-%m-%d %H:%M"))
#plot cluster statistic for mean upload speed
UpCluster <- ggplot(cluster.up, aes(help.date.time, mean.up, 
                                      colour = clusterID)) +
  theme_minimal() +
  geom_line() + 
  labs(x = "Weekdays March-May", y = "mean upload speed", col = "Cluster ID") + 
  scale_x_datetime(breaks = as.POSIXct(c("2020-03-02 15:00:00", 
                    "2020-03-03 15:00:00", "2020-03-04 15:00:00",
                    "2020-03-05 15:00:00", "2020-03-06 15:00:00"), 
                    labels = "%a"), labels = 
                     c("Mon", "Tues", "Weds", "Thurs", "Fri")) + 
  geom_point() +
  theme(legend.position = c(0.7, 0.08),
        legend.direction = "horizontal")

#export UpClusterL plot for paper
out.plot <- paste(path, "/paper/v1/figures/UpCluster.png", sep = "")
png(out.plot)
UpClusterL
dev.off()

#plot next 6 smaller clusters, but exclude 2 clusters with 1 LAD and under 100k pop
cluster.upS <- TS2020 %>%
  group_by(cluster.up, weekday, hour) %>%
  summarise(mean.up = mean(speedup))
names(cluster.upS)[1] <- "clusterID"
names(LAD.cluster.up)[1] <- "clusterID"
cluster.upS <- left_join(cluster.upS, LAD.cluster.up)
cluster.upS <- cluster.upS[which(cluster.upS$up.LADs < 10 & cluster.upS$up.LADs > 1),]
cluster.upS$clusterID <- as.factor(cluster.upS$clusterID)
#add fake dates for plotting
help.dates <- tibble(help.date.time = c(
  make_datetime(year = 2020, month = 3, day = 2),
  make_datetime(year = 2020, month = 3, day = 3),
  make_datetime(year = 2020, month = 3, day = 4),
  make_datetime(year = 2020, month = 3, day = 5),
  make_datetime(year = 2020, month = 3, day = 6)),
                     weekday = c("Mon", "Tue", "Wed", "Thu", "Fri"))
cluster.upS <- merge(cluster.upS, help.dates, by = "weekday")
cluster.upS$hour <- paste(cluster.upS$hour, ":00", sep="")
cluster.upS$help.date.time <- with(cluster.upS, as.POSIXct(paste(help.date.time, hour), format="%Y-%m-%d %H:%M"))
#plot cluster statistic for mean upload speed
UpClusterS <- ggplot(cluster.upS, aes(help.date.time, mean.up, 
                                      colour = clusterID)) +
  theme_minimal() +
  geom_line() + 
  labs(x = "Weekdays March-May", y = "mean upload speed", col = "Cluster ID") + 
  scale_x_datetime(breaks = as.POSIXct(c("2020-03-02 15:00:00", 
                    "2020-03-03 15:00:00", "2020-03-04 15:00:00",
                    "2020-03-05 15:00:00", "2020-03-06 15:00:00"), 
                    labels = "%a"), labels = 
                     c("Mon", "Tues", "Weds", "Thurs", "Fri")) + 
  geom_point() +
  theme(legend.position = c(0.8, 0.08),
        legend.direction = "horizontal")

#export UpClusterS plot for paper
#out.plot <- paste(path, "/paper/v1/figures/UpClusterS.png", sep = "")
#png(out.plot)
#UpClusterS
#dev.off()

>>>>

## Time variation plots (Figures 1 and 2)

@@

#create time variation plots for speedtests for each year
Tests19 <- count(TS2019, date)
TS2019 <- left_join(TS2019, Tests19)
names(TS2019)[13] <- "test frequency 2019"
time.var.plot2019 <- timeVariation(TS2019, pollutant = "test frequency 2019", statistic = "mean",
                                   par.settings=list(fontsize=list(text=8)))
Tests20 <- count(TS2020, date)
TS2020 <- left_join(TS2020, Tests20)
names(TS2020)[13] <- "test frequency 2020"
time.var.plot2020 <- timeVariation(TS2020, pollutant = "test frequency 2020", statistic = "mean",
                                   par.settings=list(fontsize=list(text=8)))

#export time variation plots for paper
out.plot <- paste(path, "/paper/v2_taylor_francis/figures/time.var.plot2019.png", sep = "")
png(out.plot, res = 100, width = 615, height = 615) # 72dpi default res. 480x480. 
                                                    # ((100-72)/100)*480+480 = 615 
time.var.plot2019
dev.off() # if dev.off() doesn't work try dev.set(dev.next()) 2-3 times

out.plot <- paste(path, "/paper/v2_taylor_francis/figures/time.var.plot2020.png", sep = "")
png(out.plot, res = 100, width = 615, height = 615)
time.var.plot2020
dev.off()
```

```{r}
#join clusters to TS2020
names(clusters) [1] <- "LAD19NM"
TS2020 <- left_join(TS2020, clusters)
TS2019 <- left_join(TS2019, clusters)
#remove NAs? - otherwise cannot create unified dataframes for below stats

@@

## Summarise 2020 test frequency clusters by hour of each weekday and plot

```{r }
cluster.tests <- TS2020 %>%
  group_by(cluster.tests, weekday, hour) %>%
  summarise(n.tests = n())
names(cluster.tests)[1] <- "clusterID"
cluster.tests$clusterID <- as.factor(cluster.tests$clusterID)
#add fake dates for plotting
help.dates <- tibble(help.date.time = c(
  make_datetime(year = 2020, month = 3, day = 2),
  make_datetime(year = 2020, month = 3, day = 3),
  make_datetime(year = 2020, month = 3, day = 4),
  make_datetime(year = 2020, month = 3, day = 5),
  make_datetime(year = 2020, month = 3, day = 6)),
                     weekday = c("Mon", "Tue", "Wed", "Thu", "Fri"))
cluster.tests <- merge(cluster.tests, help.dates, by = "weekday")
cluster.tests$hour <- paste(cluster.tests$hour, ":00", sep="")
cluster.tests$help.date.time <- with(cluster.tests, as.POSIXct(paste(help.date.time, hour), format="%Y-%m-%d %H:%M"))
#plot cluster statistic for number tests
TestCluster <- ggplot(cluster.tests, aes(help.date.time, n.tests, 
                                         colour = clusterID))
TestCluster + geom_line() + labs(x = "Weekdays March-May 2020") + 
  scale_x_datetime(breaks = as.POSIXct(c("2020-03-02 15:00:00", 
                    "2020-03-03 15:00:00", "2020-03-04 15:00:00",
                    "2020-03-05 15:00:00", "2020-03-06 15:00:00"), 
                    labels = "%a"), labels = 
                     c("Mon", "Tues", "Weds", "Thurs", "Fri")) + geom_point()
#summarise test frequency clusters by hour of each weekday 2019 and plot
cluster.tests19 <- TS2019 %>%
  group_by(cluster.tests, weekday, hour) %>%
  summarise(n.tests = n())
names(cluster.tests19)[1] <- "clusterID"
cluster.tests19$clusterID <- as.factor(cluster.tests19$clusterID)
#add fake dates for plotting
help.dates <- tibble(help.date.time = c(
  make_datetime(year = 2019, month = 3, day = 4),
  make_datetime(year = 2019, month = 3, day = 5),
  make_datetime(year = 2019, month = 3, day = 6),
  make_datetime(year = 2019, month = 3, day = 7),
  make_datetime(year = 2019, month = 3, day = 8)),
                     weekday = c("Mon", "Tue", "Wed", "Thu", "Fri"))
cluster.tests19 <- merge(cluster.tests19, help.dates, by = "weekday")
cluster.tests19$hour <- paste(cluster.tests19$hour, ":00", sep="")
cluster.tests19$help.date.time <- with(cluster.tests19, as.POSIXct(paste(help.date.time, hour), format="%Y-%m-%d %H:%M"))
#plot cluster statistic for number tests
TestCluster19 <- ggplot(cluster.tests19, aes(help.date.time, n.tests, 
                                         colour = clusterID))
TestCluster19 + geom_line() + labs(x = "Weekdays March-May 2019") + 
  scale_x_datetime(breaks = as.POSIXct(c("2020-03-02 15:00:00", 
                    "2020-03-03 15:00:00", "2020-03-04 15:00:00",
                    "2020-03-05 15:00:00", "2020-03-06 15:00:00"), 
                    labels = "%a"), labels = 
                     c("Mon", "Tues", "Weds", "Thurs", "Fri")) + geom_point()
```

## Summarise 2020 upload speed clusters by hour of each weekday and plot

```{r}

# plot largest 6 clusters - all over 500k pop
cluster.up <- TS2020 %>%
  group_by(cluster.up, weekday, hour) %>%
  summarise(mean.up = mean(speedup))
names(cluster.up)[1] <- "clusterID"
names(LAD.cluster.up)[1] <- "clusterID"
cluster.up <- left_join(cluster.up, LAD.cluster.up)
cluster.up <- cluster.up[which(cluster.up$up.LADs > 4),]
cluster.up$clusterID <- as.factor(cluster.up$clusterID)

# add fake dates for plotting
help.dates <- tibble(help.date.time = c(
  make_datetime(year = 2020, month = 3, day = 2),
  make_datetime(year = 2020, month = 3, day = 3),
  make_datetime(year = 2020, month = 3, day = 4),
  make_datetime(year = 2020, month = 3, day = 5),
  make_datetime(year = 2020, month = 3, day = 6)),
                     weekday = c("Mon", "Tue", "Wed", "Thu", "Fri"))
cluster.up <- merge(cluster.up, help.dates, by = "weekday")
cluster.up$hour <- paste(cluster.up$hour, ":00", sep="")
cluster.up$help.date.time <- with(cluster.up, as.POSIXct(paste(help.date.time, hour), format="%Y-%m-%d %H:%M"))

# plot cluster statistic for mean upload speed
UpCluster <- ggplot(cluster.up, aes(help.date.time, mean.up, 
                                      colour = clusterID)) +
  theme_minimal() +
  geom_line() + 
  labs(x = "Weekdays March-May", y = "mean upload speed", col = "Cluster ID") + 
  scale_x_datetime(breaks = as.POSIXct(c("2020-03-02 15:00:00", 
                    "2020-03-03 15:00:00", "2020-03-04 15:00:00",
                    "2020-03-05 15:00:00", "2020-03-06 15:00:00"), 
                    labels = "%a"), labels = 
                     c("Mon", "Tues", "Weds", "Thurs", "Fri")) + 
  geom_point() +
  theme(legend.position = c(0.7, 0.08),
        legend.direction = "horizontal")

#export UpCluster plot for paper
out.plot <- paste(path, "/paper/v2_taylor_francis/figures/UpCluster.png", sep = "")
UpCluster
ggsave(out.plot)

# EXCLUDED from paper
# plot next 6 smaller clusters, but exclude 2 clusters with 1 LAD and under 100k pop
cluster.upS <- TS2020 %>%
  group_by(cluster.up, weekday, hour) %>%
  summarise(mean.up = mean(speedup))
names(cluster.upS)[1] <- "clusterID"
names(LAD.cluster.up)[1] <- "clusterID"
cluster.upS <- left_join(cluster.upS, LAD.cluster.up)
cluster.upS <- cluster.upS[which(cluster.upS$up.LADs < 10 & cluster.upS$up.LADs > 1),]
cluster.upS$clusterID <- as.factor(cluster.upS$clusterID)

# add fake dates for plotting
help.dates <- tibble(help.date.time = c(
  make_datetime(year = 2020, month = 3, day = 2),
  make_datetime(year = 2020, month = 3, day = 3),
  make_datetime(year = 2020, month = 3, day = 4),
  make_datetime(year = 2020, month = 3, day = 5),
  make_datetime(year = 2020, month = 3, day = 6)),
                     weekday = c("Mon", "Tue", "Wed", "Thu", "Fri"))
cluster.upS <- merge(cluster.upS, help.dates, by = "weekday")
cluster.upS$hour <- paste(cluster.upS$hour, ":00", sep="")
cluster.upS$help.date.time <- with(cluster.upS, as.POSIXct(paste(help.date.time, hour), format="%Y-%m-%d %H:%M"))

# plot cluster statistic for mean upload speed
UpClusterS <- ggplot(cluster.upS, aes(help.date.time, mean.up, 
                                      colour = clusterID)) +
  theme_minimal() +
  geom_line() + 
  labs(x = "Weekdays March-May", y = "mean upload speed", col = "Cluster ID") + 
  scale_x_datetime(breaks = as.POSIXct(c("2020-03-02 15:00:00", 
                    "2020-03-03 15:00:00", "2020-03-04 15:00:00",
                    "2020-03-05 15:00:00", "2020-03-06 15:00:00"), 
                    labels = "%a"), labels = 
                     c("Mon", "Tues", "Weds", "Thurs", "Fri")) + 
  geom_point() +
  theme(legend.position = c(0.8, 0.08),
        legend.direction = "horizontal")

# The figure with the small clusters is not included in the paper
#export UpClusterS plot for paper
#out.plot <- paste(path, "/paper/v2_taylor_francis/figures/UpClusterS.png", sep = "")
#png(out.plot)
#UpClusterS
#dev.off() 
```

## Summarise 2019 upload speed clusters by hour of each weekday and plot

This is a test to compare 2020 vs. 2019 line graphs.

```{r}

# plot largest 6 clusters - all over 500k pop
cluster.up <- TS2019 %>%
  group_by(cluster.up, weekday, hour) %>%
  summarise(mean.up = mean(speedup))
names(cluster.up)[1] <- "clusterID"
names(LAD.cluster.up)[1] <- "clusterID"
cluster.up <- left_join(cluster.up, LAD.cluster.up)
cluster.up <- cluster.up[which(cluster.up$up.LADs > 4),]
cluster.up$clusterID <- as.factor(cluster.up$clusterID)

# add fake dates for plotting
help.dates <- tibble(help.date.time = c(
  make_datetime(year = 2019, month = 3, day = 4),
  make_datetime(year = 2019, month = 3, day = 5),
  make_datetime(year = 2019, month = 3, day = 6),
  make_datetime(year = 2019, month = 3, day = 7),
  make_datetime(year = 2019, month = 3, day = 8)),
                     weekday = c("Mon", "Tue", "Wed", "Thu", "Fri"))
cluster.up <- merge(cluster.up, help.dates, by = "weekday")
cluster.up$hour <- paste(cluster.up$hour, ":00", sep="")
cluster.up$help.date.time <- with(cluster.up, as.POSIXct(paste(help.date.time, hour), format="%Y-%m-%d %H:%M"))

# plot cluster statistic for mean upload speed
UpCluster2019 <- ggplot(cluster.up, aes(help.date.time, mean.up, 
                                      colour = clusterID)) +
  theme_minimal() +
  geom_line() + 
  labs(x = "Weekdays March-May", y = "mean upload speed", col = "Cluster ID") + 
  scale_x_datetime(breaks = as.POSIXct(c("2019-03-04 15:00:00", 
                    "2019-03-05 15:00:00", "2019-03-06 15:00:00",
                    "2019-03-07 15:00:00", "2019-03-08 15:00:00"), 
                    labels = "%a"), labels = 
                     c("Mon", "Tues", "Weds", "Thurs", "Fri")) + 
  geom_point() +
  theme(legend.position = c(0.7, 0.08),
        legend.direction = "horizontal")

#export UpCluster plot for paper
out.plot <- paste(path, "/paper/v2_taylor_francis/figures/UpCluster2019.png", sep = "")
UpCluster2019
ggsave(out.plot)
```

```{r eval=F}
# Not used in the paper

### 2021-03-25 src/ts_clusters_k9.Rmd
leftovers -- sorry

### Upload speed

@@

### Download speed

@@

### N. of speed tests

@@

### Upload speed diff 2019-2020

@@

### download speed diff 2019-2020

@@

## Mapping the clusters

@@

# get LA 
# this is the heaviest version:
# (i) directly from the web
#la <- readOGR("http://geoportal1-ons.opendata.arcgis.com/datasets/b6d2e15801de45328b760a4f55d74318_0.geojson?outSR={%22latestWkid%22:3857,%22wkid%22:102100}")#, layer="OGRGeoJSON")
# or, (ii) from the json I saved locally
# path.json <- paste(path, "./data/raw/Local_Authority_Districts_(April_2019)_Boundaries_UK_BFE.geojson", sep = "")
# la <- readOGR(path.json)#, layer="OGRGeoJSON")
# UK BGC: 
la <- readOGR("https://opendata.arcgis.com/datasets/0e07a8196454415eab18c40a54dfbbef_0.geojson")
# UK BFC: la <- readOGR("https://opendata.arcgis.com/datasets/1d78d47c87df4212b79fe2323aae8e08_0.geojson")

@@

>>>>

## Line graphs for upload speed (not clusters) 2019 and 2020

#test <- 
line2020 <- ts.up2020 %>% 
  mutate(day = recode(weekday, # these are dates from 2020
                            Mon=2,
                            Tue = 3,
                            Wed = 4,
                            Thu = 5,
                            Fri = 6)) %>% 
  mutate(help.date.time = make_datetime(year = 2020, month = 3, day = day),
         hour = paste0(hour, ":00"),
         help.date.time = (as.POSIXct(paste(help.date.time, hour), format="%Y-%m-%d %H:%M"))) %>% 
  group_by(help.date.time) %>%
  summarise(mean.up = mean(mean.up)) %>% 
  ggplot(aes(x=help.date.time, y=mean.up), #, group = LAD19NM, colour = LAD19NM),
         show.legend = F) + 
  geom_line() + guides(colour=FALSE) +
  xlab(2020)
  # + xlab("Year") +
  # ylab("Pareto exponent")

# library(plotly)
# ggplotly(test,
#          show.legend=F)

line2019 <- ts.up2019 %>% 
  mutate(day = recode(weekday, # these are dates from 2020
                            Mon=2,
                            Tue = 3,
                            Wed = 4,
                            Thu = 5,
                            Fri = 6)) %>% 
  mutate(help.date.time = make_datetime(year = 2020, month = 3, day = day),
         hour = paste0(hour, ":00"),
         help.date.time = (as.POSIXct(paste(help.date.time, hour), format="%Y-%m-%d %H:%M"))) %>% 
  group_by(help.date.time) %>%
  summarise(mean.up = mean(mean.up)) %>% 
  ggplot(aes(x=help.date.time, y=mean.up), #, group = LAD19NM, colour = LAD19NM),
         show.legend = F) + 
  geom_line() + guides(colour=FALSE)+
  xlab(2019)

grid.arrange(line2019, line2020, ncol = 1, nrow = 2) #legend
```

## Upload speed 2020

@@

## Download speed 2020

@@

## N. of speed tests 2020

@@

## Upload speed diff 2019-2020

@@

## download speed diff 2019-2020

@@

## Upload speed 2019

# extract names
ts.wide2019.names <- names(ts.wide2019[,-1])
ts.wide2019 <- ts.wide2019[,-1]

# standardise
ts.wide2019 <- zscore(ts.wide2019)

# convert to list for tsclust
ts.wide2019 <- split(ts.wide2019, rep(1:ncol(ts.wide2019), each = nrow(ts.wide2019)))

# k = 9
pc_k <- tsclust(ts.wide, k = 9, seed = 94L, 
                type="partitional", 
                distance = "dtw_basic", centroid = "pam", trace = T, 
                args = tsclust_args(dist = list(window.size = 20L)))
plot(pc_k)

cluster_up.2019 <- data.frame(LAD=ts.wide2019.names,
                           cluster=pc_k@cluster)
```

## Export clusters

@@

# 2019 upload cluster
out.2019.clusters <- paste(path, "/data/temp/clusters_up2019.csv", sep = "")
write_csv(cluster_up.2019, out.2019.clusters)
```

## Mapping the clusters: upload 2020

```{r include=TRUE, echo=FALSE, results= 'markup', message=FALSE, warning = FALSE, fig.height=10, fig.width=10}
# get LA

# this is the heaviest version:
# (i) directly from the web
#la <- readOGR("http://geoportal1-ons.opendata.arcgis.com/datasets/b6d2e15801de45328b760a4f55d74318_0.geojson?outSR={%22latestWkid%22:3857,%22wkid%22:102100}")#, layer="OGRGeoJSON")
# or, (ii) from the json I saved locally
# path.json <- paste(path, "./data/raw/Local_Authority_Districts_(April_2019)_Boundaries_UK_BFE.geojson", sep = "")
# la <- readOGR(path.json)#, layer="OGRGeoJSON")
# UK BGC: 
la <- readOGR("https://opendata.arcgis.com/datasets/0e07a8196454415eab18c40a54dfbbef_0.geojson")
# UK BFC: la <- readOGR("https://opendata.arcgis.com/datasets/1d78d47c87df4212b79fe2323aae8e08_0.geojson")

@@

## Mapping the clusters: upload 2019

```{r include=TRUE, echo=FALSE, results= 'markup', message=FALSE, warning = FALSE, fig.height=10, fig.width=10}
# get LA

# ggplot2 maps
la.f <- broom::tidy(la, region = "lad19nm")
la.f <- merge(la.f, cluster_up.2019, by.x = "id", by.y = "LAD")
la.f <- la.f[order(la.f$order),] # if i don't order merge.nuts.f loses order and the map has gaps

ggplot(la.f, aes(x = long, y = lat)) +
  geom_polygon(aes( group = group, fill = as.factor(cluster))) +
  #labs(title = "Upload clusters") +
  scale_fill_brewer(palette="Set1", 
                    direction = -1) +
  geom_text_repel( data=cities %>% arrange(pop) %>% tail(10), aes(x=long, y=lat, label=name), size=4) +
  geom_point( data=cities %>% arrange(pop) %>% tail(10), aes(x=long, y=lat), color="black", size=1) +
  guides(fill=guide_legend(title="Clusters")) +
  theme_void()

# Run only if needed
# out.path.map <- paste0(path, "/paper/v2_taylor_francis/figures/map.up.2019.clusters.png")
# ggsave(out.path.map)
#width = 210, #A4
#height = 297, #A4
#units = "mm")
```
